Marginally-Stable Thermal Equilibria of Rayleigh-B\'enard Convection

### 2021-08-31 publication_materials/ms_rbc.tex
PRL: final draft

\section*{Acknowledgments}
This paper is dedicated to Charlie Doering, who greatly influenced the way many of us think about Rayleigh-Benard convection.
DL met Charlie as a WHOI GFD summer fellow, and has difficulty imagining Walsh Cottage without Charlie's friendly and open scientific style, and enthusiasm for softball.
The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions.
We would also like to thank Charlie Doering and Baole Wen for the tabulated DNS and ECS data for Figure~\ref{fig:nu_vs_ra}.
We thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GIDs s2276.

>>>>

\section*{Acknowledgments}
We would like to thank Charlie Doering, who greatly influenced the way many of us think about Rayleigh-B\'enard convection.
Some of the ideas in this work came from discussions with Charlie at Walsh Cottage during the WHOI GFD summer programs; it is difficult to imagining Walsh Cottage without Charlie's friendly and open scientific style, and enthusiasm for softball.
The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions.
We would also like to thank Charlie Doering and Baole Wen for the tabulated DNS and ECS data for Figure~\ref{fig:nu_vs_ra}.
We thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GIDs s2276.
